---
title: "William Amorim's CV"
author: William Amorim
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: false
output:
  pagedown::html_resume:
    css: [ 'dd_cv.css', 'custom.css','resume']
    self_contained: true
#knit: pagedown::chrome_print      
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE
)
```



```{r metathis, echo=FALSE}
library(metathis)
meta() %>%
  meta_name("github-repo" = "williamorim/resume") %>% 
  meta_social(
    title = "William Amorim CV",
    description = paste(
      "CV made with the packages RMarkdown, pagedown, datadrivencv."
    ),
    url = "https://williamorim.github.io/resume/index.html",
    image = "https://williamorim.github.io/resume/img/share-card.png",
    image_alt = paste(
      "William Amorim CV"
    ),
    og_type = "website",
    og_author = "William Amorim"
  )
```
<!-- inicio academic icons -->
<link rel="stylesheet" href="https://cdn.jsdelivr.net/gh/jpswalsh/academicons@1/css/academicons.min.css">
<!-- final academic icons -->

 
<!-- inicio font awesome -->
<script src="https://kit.fontawesome.com/1f72d6921a.js" crossorigin="anonymous"></script>

 
<!-- final font awesome -->

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis',
  echo = FALSE
)

library(magrittr) # For the pipe
source("cv_printing_functions.r")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1tDDF9v4cO18nd2JZur5zq7y-7Xb7f4KsBhjJD_WUneE",  
  pdf_mode = params$pdf_mode
)

CV$entries_data <- CV$entries_data %>% dplyr::filter(in_resume == TRUE)

```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================

CONTACT {#contact}
--------------------------------------------------------------------------------

- <i class="fa fa-envelope"></i> wamorim@curso-r.com

- <i class="fa fa-github"></i> [GitHub: `@`williamorim](https://github.com/williamorim)

- <i class="fa fa-external-link-alt"></i> <a href='http://lattes.cnpq.br/9062934205884130'> Lattes </a> 

- <i class="fa fa-home"></i> [Site]()

<br>

> I do not have social networks. You can find me on my webpage.

BOOK {#software}
--------------------------------------------------------------------------------

<i class="fas fa-box-open"></i> [Ciência de Dados em R](https://livro.curso-r.com/) 


Programming {#skills}
--------------------------------------------------------------------------------

<i class="fab fa-r-project"></i> `R` 

<i class="fas fa-table"></i> `tidyverse` and `shiny`

<i class="fas fa-code-branch"></i> `Git` 

<i class="fab fa-html5"></i> `HTML`, `CSS` and `JavaScript`

Disclaimer {#disclaimer}
--------------------------------------------------------------------------------


```{r}
if(params$pdf_mode){
  cat("View this CV online with links at https://williamorim.github.io/resume/")
} else {
  cat("<i class='fas fa-download'></i> [Download this resume in PDF](https://williamorim.github.io/resume/index.pdf)")
}
```

This resume was made with the R package [**pagedown**](https://github.com/rstudio/pagedown)

This resume model was developed by [Beatriz Milz](https://github.com/beatrizmilz/resume)

Code available on <i class="fa fa-github"></i> [GitHub](https://github.com/williamorim/resume)

Last updated on `r Sys.Date()`


Main
================================================================================

William Nilson de Amorim {#title}
--------------------------------------------------------------------------------

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('education')
```

Professional {data-icon=suitcase data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('professional')
```

Selected Works {data-icon=laptop}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('works')
```

Research Projects {data-icon=laptop}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('research_projects')
```

<br>
<br>

Teaching Experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

:::aside

### **Languages**

**Portuguese**: Native

**English**: Proficient

**Spanish**: Beginner

**French**: Beginner

<br>

### **Interests**

Stories

Science

Writing

Strategy games

Soccer

Piano

:::

```{r}
CV %<>% print_section('teaching_experience')
```

